PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-09-14 qfenv_paper/qf_environment.tex
Nitya's edits on intro

The most dramatic change in galaxy properties during the past eight
billion years has been a remarkable decline in the star-formation rate
of galaxies in the Universe (\citealt{hopkins06a}).  This decline
appears dominated by decreases in the rates of star-formation of
individual galaxies (\cite{Noeske:2007aa}). There is evidence that a
large fraction of the decline is associated with strongly
infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).  The
decline does not appear to be due to the quenching of a large
fractions of the star-forming population, as reflected in observations
of the stellar mass function of quiescent and star-forming galaxies
(\citealt{Blanton:2006aa, bundy06a, borch06a, Moustakas:2013aa}).  These
findings leave little room for the participation of
environmentally-driven quenching in the global census of
star-formation.  As \cite{cooper08a} and others have pointed out,
because the environmental dependence of total star-formation rates at
fixed redshift is relatively small, environmentally effects are
unlikely to cause the overall star-formation rate decline.

Thus, the impact of environment on galaxy formation has to be
interpreted on top of the background of this overall decline affecting
galaxies in all environments. The most straightforward investigation
would directly determine the star-forming properties of galaxies as
a function of environment, stellar mass and redshift in a single,
consistently analyzed data set. This analysis can reveal how galaxies
are quenched in the universe over time, quantitatively establish the
contribution of environmental effects to the overall trends, and
reveal whether those trends happen equally in all environments.
However, such an analysis has not been done previously due to the lack
of sufficiently large samples. In this paper, we apply this approach
using the Prism Multi-object Survey (PRIMUS; \cite{Coil:2011aa}, 
\cite{Cool:2013aa}), the largest available redshift survey covering the epochs
between $0<z<1$.

@@

Meanwhile in their mass bin most comparable to $\mathcal{M}_{\rm{fid}} \sim 10^10.5 \mathcal{M}_{\odot}$ ($10^{10.3} \mathcal{M}_{\odot} - 10^{10.8} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ evolves by $\sim 0.1$ from $z = 0.5$ to $0.25$ for group galaxies and by $\sim 0.3$ from $z=0.55$ to $0.3$ for isolated galaxies as presented in Figure \ref{fig:qffit_comp}. Altogether, with mass bins beyond the fiducial masses we explore, \cite{Iovino:2010aa} find a strong mass dependence with $f_{\rm{Q}}$ evolving significantly more in lower mass bins. While our sample from PRIMUS provides larger statistics than zCOSMOS, the mass-completeness limits we impose on our sample limits the mass range we probe (e.g. $\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin). Consequently our results cannot dismiss mass dependence in the $f_{\rm{Q}}$ evolution at lower masses.

@@

The more recent \cite{Kovac:2014aa} provides larger statistics with $2,340$ galaxies in their lower redshift bin ($0.1 < z < 0.4$) and $2,448$ galaxies in their higher redshift bin ($0.4 < z < 0.7$). Although their sample falls short of our PRIMUS sample, which contains over two times the number of galaxies, the \cite{Kovac:2010aa} sample provides a more stable comparison.  Once their results are adjusted for the different galaxy classification, we find that their overall $f_{\rm{Q}}$ is more or less consistent with our overall $f_{\rm{Q}}$. However, it is difficult to explain the significant discrepancies in the $f_{\rm{Q}}$ evolutionary trends.
% zCOSMOS has more precise redshift but PRIMUS has it beat in terms of sample size and coverage of the sky 5.5 deg^2 vs 1.7 deg^2
% Kovac: 1.7 deg^2, 0.1 < z < 0.4 2340 and 0.4 < z < 0.7 2448. Most of the data points have errors of +/- 0.1, at least +/-0.05
% Iovino: 1.7 deg^2  617 galaxies in 10.3 < M < 10.8 and 0.1 < z < 0.6. Errors are +/1 0.1

>>>>

The most dramatic change in galaxy properties during the past eight
billion years has been a remarkable decline in the star-formation rate
of galaxies in the Universe (\citealt{hopkins06a}).  This decline
appears dominated by decreases in the rates of star-formation of
individual galaxies (\cite{Noeske:2007aa}). There is evidence that a
large fraction of the decline is associated with strongly
infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).  The
decline does not appear to be due to the quenching of a large
fraction of the star-forming population, as reflected in observations
of the stellar mass function of quiescent and star-forming galaxies
(\citealt{Blanton:2006aa, bundy06a, borch06a, Moustakas:2013aa}).  These
findings leave little room for the participation of
environmentally-driven quenching in the global census of
star-formation.  As \cite{cooper08a} and others have pointed out,
because the environmental dependence of total star-formation rates at
fixed redshift is relatively small, environmentally effects are
unlikely to cause the overall star-formation rate decline.

Thus, the impact of environment on galaxy formation has to be
interpreted on top of the background of this overall decline affecting
galaxies in all environments. The most straightforward investigation
would be to directly determine the star-forming properties of galaxies as
a function of environment, stellar mass and redshift in a single,
consistently analyzed data set. This analysis can reveal how galaxies
are quenched in the universe over time, quantitatively establish the
contribution of environmental effects to the overall trends, and
reveal whether those trends happen equally in all environments.
However, such an analysis has not been done previously due to the lack
of sufficiently large samples. In this paper, we apply this approach
using the Prism Multi-object Survey (PRIMUS; \cite{Coil:2011aa}, 
\cite{Cool:2013aa}), the largest available redshift survey covering the epochs
between $0<z<1$.

@@

Meanwhile in their mass bin most comparable to $\mathcal{M}_{\rm{fid}} \sim 10^{10.5} \mathcal{M}_{\odot}$ ($10^{10.3} \mathcal{M}_{\odot} - 10^{10.8} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ evolves by $\sim 0.1$ from $z = 0.5$ to $0.25$ for group galaxies and by $\sim 0.3$ from $z=0.55$ to $0.3$ for isolated galaxies as presented in Figure \ref{fig:qffit_comp}. Altogether, with mass bins beyond the fiducial masses we explore, \cite{Iovino:2010aa} find a strong mass dependence with $f_{\rm{Q}}$ evolving significantly more in lower mass bins. While our sample from PRIMUS provides larger statistics than zCOSMOS, the mass-completeness limits we impose on our sample limits the mass range we probe (e.g. $\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin). Consequently our results cannot dismiss mass dependence in the $f_{\rm{Q}}$ evolution at lower masses.

@@

The more recent \cite{Kovac:2014aa} provides larger statistics with $2,340$ galaxies in their lower redshift bin ($0.1 < z < 0.4$) and $2,448$ galaxies in their higher redshift bin ($0.4 < z < 0.7$). Although their sample falls short of our PRIMUS sample, which contains over two times the number of galaxies, the \cite{Kovac:2014aa} sample provides a more stable comparison.  Once their results are adjusted for the different galaxy classification, we find that their overall $f_{\rm{Q}}$ is more or less consistent with our overall $f_{\rm{Q}}$. However, it is difficult to explain the significant discrepancies in the $f_{\rm{Q}}$ evolutionary trends.
% zCOSMOS has more precise redshift but PRIMUS has it beat in terms of sample size and coverage of the sky 5.5 deg^2 vs 1.7 deg^2
% Kovac: 1.7 deg^2, 0.1 < z < 0.4 2340 and 0.4 < z < 0.7 2448. Most of the data points have errors of +/- 0.1, at least +/-0.05
% Iovino: 1.7 deg^2  617 galaxies in 10.3 < M < 10.8 and 0.1 < z < 0.6. Errors are +/1 0.1
